\documentclass{uofsthesis-cs}

% \usepackage{algorithm}
\usepackage{tikz}
\usetikzlibrary{arrows,snakes,backgrounds}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usetikzlibrary{patterns}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{listings}

\usepackage[linesnumbered,ruled]{algorithm2e}

% Documentation for the uofsthesis-cs class is given in uofsthesis-cs.dvi
% 
% It is recommended that you read the CGSR thesis preparation
% guidelines before proceeding.
% They can be found at http://www.usask.ca/cgsr/thesis/index.htm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FRONTMATTER - In this section, specify information to be used to
% typeset the thesis frontmatter.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% THESIS TITLE
% Specify the title. Set the capitalization how you want it.
\title{HCPC: Human centric program comprehension by grouping static execution scenarios}

% AUTHOR'S NAME
% Your name goes here.
\author{Avijit Bhattacharjee}

% DEGREE SOUGHT.  
% Use \MSc or \PhD here
\degree{\MSc}         

% THESIS DEFENCE DATE
% Should be month/year, e.g. July 2004
\defencedate{July/2021}


% NAME OF ACADEMIC UNIT
%
% The following two commands allow you to specify the academic unit you belong to.
% This will appear on the title page as
% ``<academic unit> of <department>''.
% So if you are in the division of biomedical engineering you would need to do:
% \department{Biomedical Engineering}
% \academicunit{Division}
%
% The default is ``Department of Computer Science'' if these commands
% are not given.
%
% If you are in a discipline other than Computer Science, uncomment the following line and
% specify your discipline/department.  Default is 'Computer Science'.
% \department{If not Computer Science, put the name of your department here}

% If you are not in a department, but say, a division, uncomment the following line.
% \academicunit{Put the type of academic unit you belong to here, e.g. Division, College}


% PERMISSION TO USE ADDRESS
%
% If you are not in Comptuer Science you will want to change the
% address on the Permission to Use page.  This is done using the
% \ptuaddress{}.  Example:
%
% \ptuaddress{Head of the Department of Computer Science\\
% 176 Thorvaldson Building\\
% 110 Science Place\\
% University of Saskatchewan\\
% Saskatoon, Saskatchewan\\
% Canada\\
% S7N 5C9
% }

% ABSTRACT
\abstract{
New members of a software team can struggle to locate use requirements if proper software engineering principles are not practiced. Reading through code, finding relevant methods, classes and files take a significant portion of software development time. Many times developers have to fix issues in code written by others. Having good tool support for this code browsing activity can reduce human effort and increase overall developer productivity. To help program comprehension activities,  building an abstract code summary of a software system from the call graph is an active research area. A call graph is a visual representation of caller-callee relationships between different methods of a software project. Call graphs can be difficult to comprehend for a larger code-base. The motivation is to extract the essence from the call graph by finding execution scenarios from a call graph and then cluster them together by concentrating the information in the code-base. Later, different techniques are applied to label nodes in the abstract code summary tree. In this thesis, we focus on static call graphs for creating an abstract code summary tree as it clusters all possible program scenarios and groups similar scenarios together. Previous work on static call graph clusters execution paths and uses only one information retrieval technique without any feedback from developers. First, to advance existing work, we introduced new information retrieval techniques alongside human-involved evaluation. We found that developers prefer node labels generated by terms in method names with TFIDF (term frequency-inverse document frequency). Second, from our observation, we introduced two types of information (text description using comments and execution patterns) to abstraction nodes for better insight on what execution scenarios they cover. Finally, we introduced an interactive software tool which can be used to browse the code-base in a guided way by targeting specific units of the source code. In the user study, we found developers can use our tool to overview a project alongside finding help for doing particular jobs such as locating relevant files and understanding relevant domain knowledge.
}

% THESIS ACKNOWLEDGEMENTS -- This can be free-form.
\acknowledgements{
First, I would like to express my gratitude to my supervisor Dr. Banani Roy for her constant guidance, suggestions, motivation and patience during my thesis work. I am grateful to Dr. Kevin A. Schneider for his support, feedback and guidance to shape my thesis work at the end of my program when Dr. Banani was on leave for family emergency. I am grateful to Dr. Chanchal K. Roy for his support, feedback during my program.


I would like to thank Dr. Gordon McCalla, Dr. Shahedul Khan, and Dr. Madison Klarkowski for their willingness to take part in the evaluation and advisement of my thesis. In addition, I am grateful to them for their valuable feedback, and suggestions.  

I would like to thank anonymous reviewers for their valuable comments and feedback which helped to improve this thesis work.

Special thanks goes to the Software Research Lab (SRLab) and Interactive Software Engineering (iSE) lab members for the good time we have together during daily discussion at Tim's, playing cricket, soccer during summer. In particular, I would like to thank Dr. Manishankar Mondal, Dr. Masudur Rahman, Amit Kumar Mondal, Daniel Abediny, Muhammad Mainul Hossain, CM Khaled Saifullah, Shamse Tasnim Cynthia, Zonayed Ahmed, Naz Zarren Oishie, Shamima Yeasmin, Farouq Al-omari, Sristy Sumana Nath, Golam Mostaeen, Kawser Wazed Nafi, Debasish Chakroborti, Saikat Mondal, Md Nadim, Md Shamimur Rahman, Judith Islam, Tonny Kar, Md. Abdul Awal, Hamid Khodabandehloo.

I would like to thank the Computer Science department of the University of Saskatchewan for their financial assistance through scholarships, awards, bursaries which helped me to focus on this thesis work. Moreover, I would like to thank all the staffs of the Department for their constant support. In particular, I would like to thank Sophie Findlay, Heather Webb, Greg Oster, Shakiba Jalal, James Ko, Jeff Long, Maurine Powell, and Cary Bernath.

I would like to thank my friends and family who instead of being thousand miles apart was available for me when I needed them. In addition, I would like to thank Afsana Sultana Ruma, Kinkshuk Kalyan Sarker, Tanushree Das and Ushasi Srija Chakroborti for their time, love and mental support during my stay in Saskatoon. 
}

% THESIS DEDICATION -- Also free-form.  If you don't want a dedication, comment out the following
% line.
\dedication{

I dedicate this thesis to my mother Bina Bhattacharjee, my father Arun Kumar Bhattacharjee and my younger brother Bishwajit Bhattacharjee, who always believed in me and inspired me to become the best version of myself.
}

% LIST OF ABBREVIATIONS - Sample  
% If you don't want a list of abbreviations, comment the following 4 lines.
\loa{\abbrev{ACST}{Abstract code summary tree}
\abbrev{EP}{Execution Path}
\abbrev{IR}{Information Retrieval}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF FRONTMATTER SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Typeset the title page
\maketitle

% Typeset the frontmatter.  
\frontmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIRST CHAPTER OF THESIS BEGINS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}

\input{chapters/intro}


% Since thesis chapters are very long and there are a lot of them, it is recommended
% that you put each chapter in a separate .tex file and \input each one of them
% in order.  For example:
%
% \input chap1.tex
% \input chap2.tex
% ...
%
% The \input command inserts contents of the specified file at the point of the command.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUBSEQUENT CHAPTERS (or \input's)  GO HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Background}
\input{chapters/background}

% \chapter{Related Work}
% \input{chapters/related_work}

\chapter{ Labeling abstraction nodes and human evaluation}
\input{chapters/hla1}

\chapter{ Providing summary and significant patterns for abstraction nodes}
\input{chapters/hla2}

\chapter{Finding effectiveness of abstract code summary tree}
\input{chapters/hla3}

\chapter{Conclusion and Future Plans}
\input{chapters/conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Bibliograpy should go here. BEFORE appendices!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Typeset the Bibliography.  The bibliography style used is "plain".
% Optionally, you can specify the bibliography style to use:
% \uofsbibliography[stylename]{yourbibfile}

\uofsbibliography{reference}

% If you are not using bibtex, comment the line above and uncomment
% the line below.  
%Follow the line below with a thebibliography environmentand bibitems.  
% Note: use of bibtex is usually the preferred method.

%\uofsbibliographynobibtex


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDICES
%
% Any chapters appearing after the \appendix command get numbered with
% capital letters starting with appendix 'A'.
% New chapters from here on will be called 'Appendix A', 'Appendix B'
% as opposed to 'Chapter 1', 'Chapter 2', etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Activate thesis appendix mode.
\uofsappendix

% Put appendix chapters in the appendices environment so that they appear correcty
% in the table of contents.  You can use \input's here as well.
\begin{appendices}

\chapter{Simple Calculator program to demonstrate the clustering approach}
\label{appendix:calculator}

\lstinputlisting{appendix/calculator.py}

\end{appendices}

\end{document}
